Robust Clustering for Ad Hoc Cognitive Radio Network

### 2017-04-17 journal-draft/ettdoc.tex
change the expression of weight p

\begin{equation}
t_{ij} = \frac{q_{ij}}{|C_i|} - p_i(C_i)
\end{equation}
where constant $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
%$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
$p_i(C_i)$ is the size-related weight, which reflects the deviation of $C_i$'s size from the desired size.
Assuming $\delta$ is the desired size, then there is
$$
p_i(C_i) = \left\{ \begin{array}{rl}
0 &\mbox{ if $|C_i|=\delta$} \\
\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
\vdots
\end{array} \right.
$$
where $\rho_1, \rho_2, \cdots$ are positive values and these is $\rho_2> \rho_1>0$.

@@

%Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
When $t_{ij}$ is replaced by $\frac{q_{ij}}{|C_i|} - p_i(C_i)$, the objective function becomes,
\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p_i(C_i)) \\
\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
The sum of the first items is the sum of CCs of all the chosen clusters.
As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.

>>>>

\begin{equation}
t_{ij} = \frac{q_{ij}}{|C_i|} - p_i(C_i)
\end{equation}
where constant $q_{ij}= |K(C_i)|$ when node $j\in C_i$, and $q_{ij}= 0$ when node $j\notin C_i$.
%$|K(C_i)|$ is the number of CCs of cluster $C_i$, and $|C_i|$ is the size of cluster $C_i$.
$p(C_i)$ is the size-related weight, which reflects the deviation of $C_i$'s size from the desired size.
Assuming $\delta$ is the desired size, then the weight $p$ is decided according to the different cluster sizes, \ie 1,2, $\cdots$, $\sigma$.  
$$
p(C_i) = \left\{ \begin{array}{rl}
0 &\mbox{ if $|C_i|=\delta$} \\
\rho_1 &\mbox{if $||C_i|-1|=\delta$} \\
\rho_2 &\mbox{if $||C_i|-2|=\delta$} \\
\vdots\\
\rho_\sigma &\mbox{if $||C_i|-\sigma|=\delta$} \\
\end{array} \right.
$$
where $\rho_1, \rho_2, \cdots, \rho_\sigma$ are positive values and these is $\sigma > \rho_2> \rho_1>0$.

@@

%Now we examine the objective function to see whether it in line with the goal to maximize the total number of CCs meanwhile consider the restriction on the cluster size.
When $t_{ij}$ is replaced by $\frac{q_{ij}}{|C_i|} - p(C_i)$, the objective function becomes,
\begin{equation}
\begin{aligned}
     &\max\limits_{y_i, x_{ij}} && \Sigma_{j=1}^N\Sigma_{i=1}^M (y_i\cdot \frac{q_{ij}}{|C_i|} - y_i\cdot p(C_i)) \\
\notag
\end{aligned}
\label{centralized_opt}
\end{equation}
The sum of the first items is the sum of CCs of all the chosen clusters.
As to the second item, when $w_i$ is 1 ($C_i$ is chosen) and $|C_i|\neq\delta$, it will be negative, which contradicts the direction of the optimization.
Thus the second item discourages the appearance the clusters whose sizes deviate from $\delta$.
